### 2017-07-17 Writing/draft.tex
PAUP: added rearrangement limit to 5M but increased reps to 500
Updated draft

Up to this date, a lot of work has been done on character correlation \textit{per se}, but focussing mainly on how to measure correlation between characters to detect patterns of coevolution \citep{Lande1983,Maddison1990,Pagel1994,Pagel2006,Grabowski2016}.
However, only several attempts have been made on the actual effect of characters correlation on phylogenetic inference with two notable exceptions of \cite{Davalos01072014} on empirical data and \cite{ZouConvergence} on molecular data.
It is thus still unclear what will be the effect of characters correlation on phylogenetic inference: how does these correlation really affect topology?
Additionally, because of the nature of discrete morphological characters and organisms morphology, correlation is expected to rise through both combinatorics properties of the characters or simply through evolutionary processes.
What is the effect of these two sources of correlations and can we (should we) avoid them?

@@

@@

\subsection{Empirical morphological matrices}

We applied the same procedure described above (without the morphological matrices simulation) to 100 empirical matrices downloaded from TreeBASE (\url{http://treebase.org/}).
The 100 matrices where selected to be the most representative of empirical work with discrete morphological data: with randomly selected matrices with more than 100 each, published between 1985 and 2013 and covering 19 taxonomic classes within 6 phyla (Chordata, Arthropoda, Annelida, Angiosperm, Gymnosperm and Pteridophyta).
The full list of matrices is available in the supplementary materials @@@.

>>>>

Up to this date, a lot of work has been done on character correlation \textit{per se}, but focussing mainly on how to measure correlation between characters to detect patterns of coevolution \citep{Lande1983,Maddison1990,Pagel1994,Pagel2006,Grabowski2016}.

Also \cite{goswami2010}.

However, only several attempts have been made on the actual effect of characters correlation on phylogenetic inference with two notable exceptions of \cite{Davalos01072014} on empirical data and \cite{ZouConvergence} on molecular data.
It is thus still unclear what will be the effect of characters correlation on phylogenetic inference: how does these correlation really affect topology?
Additionally, because of the nature of discrete morphological characters and organisms morphology, correlation is expected to rise through both combinatorics properties of the characters or simply through evolutionary processes.
What is the effect of these two sources of correlations and can we (should we) avoid them?

@@

 % "hsearch addseq=random nreps=500 rseed=01234 rearrlimit=5000000;"

Due to cluster hardware requirements an to save some time, when chains didn't converged and the runs exceeded 10GB, we aborted the MCMC and computed the consensus tree from the uncoverged chains.
In practice, these chains got stuck at an ASDS around (but not below) 0.01.

@@

% \subsection{Empirical morphological matrices}

% We applied the same procedure described above (without the morphological matrices simulation) to 100 empirical matrices downloaded from TreeBASE (\url{http://treebase.org/}).
% The 100 matrices where selected to be the most representative of empirical work with discrete morphological data: with randomly selected matrices with more than 100 each, published between 1985 and 2013 and covering 19 taxonomic classes within 6 phyla (Chordata, Arthropoda, Annelida, Angiosperm, Gymnosperm and Pteridophyta).
% The full list of matrices is available in the supplementary materials @@@.
